---
title: 'Academic: the website builder for Hugo'
subtitle: 'Create a beautifully simple website in under 10 minutes :rocket:'
summary: Create a beautifully simple website in under 10 minutes.
authors:
- admin
# tags:
# - Academic
# - 开源
categories:
- Demo
- 教程
date: "2020-10-16T00:00:00Z"
lastmod: Sys.time()
featured: false
draft: false

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr); library(sf)

nc <- st_read(system.file("shape/nc.shp", package="sf")) %>% 
  st_transform(6542)

misc_polygon <- nc[5,]

misc_polygon_centroid <- st_centroid(misc_polygon)

plot(misc_polygon$geometry)
plot(misc_polygon_centroid$geometry, add = T, col = 'red')
```


def.par <- par(no.readonly = TRUE)

par(mfrow = c(2, 3))
plot(misc_polygon$geometry)
plot(misc_polygon_centroid$geometry, add = T, col = 'red')

centr_buff <- misc_polygon_centroid %>% 
  st_buffer(30000) %>% 
  st_cast('POINT')

plot(misc_polygon$geometry)
plot(misc_polygon_centroid$geometry, add = T, col = 'red')
plot(centr_buff$geometry, add = T)

# There are 30 vertices per quarter of the circle (this can be changed, see ?sf::st_buffer)
##  For a staight line through the center, we want to connect vertices
##    opposite from one another (vertex 1 and 61 are a pair; vertex 2 and 62; etc.)
##  We only need to calculate these one way (line connecting 1 to 61 only, no need for 61 to 1)

# sf::st_union is not a "tidy" function; we want to combine points by row here,
#   but sf::st_union provides a Cartesian product (all combinations of points).
#   geotidy::st_union does what we want -- a row-wise union.

endpoints <- geotidy::st_union(st_geometry(slice(centr_buff, 1:60)),
                               st_geometry(slice(centr_buff, 61:120)))

# cast the start/end points to a LINESTRING
lines <- endpoints %>% 
  st_cast('LINESTRING')

plot(misc_polygon$geometry)
plot(centr_buff$geometry, add = T)
plot(lines, add = T)
plot(misc_polygon_centroid$geometry, add = T, col = 'red')

# create simple feature collection with the correct CRS and convert to simple features
lines <-  lines %>% 
  st_sfc(crs = 6542) %>%
  st_as_sf()


lines <- lines %>% 
  st_intersection(st_geometry(misc_polygon))

plot(misc_polygon$geometry)
plot(centr_buff$geometry, add = T)
plot(lines$x, add = T, col = 'blue')
plot(misc_polygon_centroid$geometry, add = T, col = 'red')

winner <- lines %>% 
  slice(., which.min(st_length(.)))

plot(misc_polygon$geometry)
plot(centr_buff$geometry, add = T)
plot(lines$x, add = T, col = 'blue')
plot(misc_polygon_centroid$geometry, add = T, col = 'red')
plot(winner, add = T, col = 'red')

plot(type = 'n')

par(def.par)






st_misc_polygon_verts <- misc_polygon %>% 
  st_cast('POLYGON') %>% 
  st_cast('POINT')

closest <- misc_polygon_verts %>% 
  st_distance(misc_polygon_centroid) %>% 
  which.min()

closest <- misc_polygon_verts %>% 
  slice(closest)

plot(misc_polygon$geometry)
plot(misc_polygon_centroid$geometry, add = T, col = 'red')
plot(closest$geometry, add = T, col = 'blue')



nearest <- misc_polygon_verts %>% 
  st_nearest_points(misc_polygon_centroid) %>% 
  st_as_sf() %>% 
  mutate(length = st_length(x)) %>% 
  slice(which.min(length))

plot(nearest$x, add = T, lty = 'dashed')



centroid_buff %>% 
